---
title: "Study2_Trump_Hillary"
author: "Angel V. Jimenez"
date: "24 July 2019"
output:
  word_document: default
  pdf_document: default
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# DATASET (PRE-TEST FOR STUDY 1 FROM KAKKAR AND SIVANATHAN, 2017)

This is the data used by Kakkar and Sivanathan after applying their exclusion criteria. The data can be found here: https://osf.io/5xez4/ 
```{r}
# Open dataset
data<-read.csv("dataset_study2a.csv")
# Select data for comparing Hillary Clinton with Donald Trump
Hillary<-data[ which(data$condi=='0'),] 
# Select data for comparing Donald Trump with Hillary Clinton
Trump<-data[ which(data$condi=='1'),] 
```

# DESCRIPTIVE STATISTICS NOT REPORTED BY KAKKAR AND SIVANATHAN (2017)

```{r}
#Age
mean(data$age) # M = 37.55
sd(data$age) # SD = 12.41
range(data$age) # 18-84
# Histogram for age
breaks<-c(15, 25, 35,  45,  55,  65,75,85)
hist(data$age,
     main="Histogram for Age",
     xlab="Age",
     border="blue",
     col="green",
     breaks = breaks,
     xlim=c(10,90),
     ylim=c(0,50),
     prob = FALSE,
     xaxt ="n")
axis(side=1, at=seq(15,85, 10), labels=seq(15,85,10))

#Gender
library(plyr)
count(data$gender) # 55 male, 65 female (assuming that 1=male, 2=female, not specified in the datafile)

#Political Ideology 
mean(data$polit_1)
sd(data$polit_1)
range(data$polit_1)


hist(data$polit_1,
     main="Histogram for Political Ideology (1=Republican, 7=Democrat)",
     xlab="Democrat Ideology",
     border="blue",
     col="green",
     xlim=c(1,7),
     ylim=c(0,30),
     prob = FALSE)
```
# CORRELATION DOMINANCE-PRESTIGE FOR HILLARY CLINTON
```{r}
cor(Hillary$dom, Hillary$ptg)
```

```{r}
library(ggplot2)
library(ggExtra)

Hillary_ptg_dom<-ggplot(Hillary, aes(x=dom, y=ptg)) +
  geom_point()+
  geom_smooth(method="lm", level=0.89, formula=y~x)+
  theme(strip.text.x = element_text(color="black", size=20,face="bold" ))+ 
  ylab("Average Prestige Ratings")+
  xlab("Average Dominance Ratings")+
  theme (axis.title.y = element_text(color="black", size=20, face="bold"), axis.title.x = element_text(color="black", size=24, face="bold"))+theme_bw()+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_x_continuous(breaks = seq(1, 7, by = 1))+
  scale_y_continuous(breaks = seq(1, 7, by = 1))+
  ggtitle("Hillary Clinton")

a<-ggMarginal(Hillary_ptg_dom, type = "histogram")

```




# CORRELATION DOMINANCE-PRESTIGE FOR DONALD TRUMP

```{r}
cor(Trump$dom, Trump$ptg)
```

```{r}
library(ggplot2)
library(ggExtra)

Trump_ptg_dom<-ggplot(Trump, aes(x=dom, y=ptg)) +
  geom_point()+
  geom_smooth(method="lm", level=0.89, formula=y~x)+
  theme(strip.text.x = element_text(color="black", size=20,face="bold" ))+ 
  ylab("Average Prestige Ratings")+
  xlab("Average Dominance Ratings")+
  theme (axis.title.y = element_text(color="black", size=20, face="bold"), axis.title.x = element_text(color="black", size=24, face="bold"))+theme_bw()+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_x_continuous(breaks = seq(1, 7, by = 1))+
  scale_y_continuous(breaks = seq(1, 7, by = 1))+
  ggtitle("Donald Trump")

b<-ggMarginal(Trump_ptg_dom, type = "histogram")

```

```{r}
library(gridExtra)
grid.arrange(a, b, ncol=2) 
```


# CORRELATION LIBERAL IDEOLOGY- PERCEPTIONS OF HILLARY CLINTON AS PRESTIGIOUS

```{r}
cor(Hillary$ptg, Hillary$polit_1)
```

```{r}
library(ggplot2)
library(ggExtra)

Hillary_ptg_polit<-ggplot(Hillary, aes(x=polit_1, y=ptg)) +
  geom_point()+
  geom_smooth(method="lm", level=0.89, formula=y~x)+
  theme(strip.text.x = element_text(color="black", size=20,face="bold" ))+ 
  ylab("Average Prestige Ratings")+
  xlab("Liberal Ideology")+
  theme (axis.title.y = element_text(color="black", size=20, face="bold"), axis.title.x = element_text(color="black", size=24, face="bold"))+theme_bw()+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_x_continuous(breaks = seq(1, 7, by = 1))+
  scale_y_continuous(breaks = seq(1, 7, by = 1))+
  ggtitle("Hillary Clinton")

c<-ggMarginal(Hillary_ptg_polit, type = "histogram")

```


# CORRELATION LIBERAL IDEOLOGY - PERCEPTIONS OF DONALD TRUMP AS PRESTIGIOUS
```{r}
cor(Trump$ptg, Trump$polit_1)
```
```{r}
library(ggplot2)
library(ggExtra)

Trump_ptg_polit<-ggplot(Trump, aes(x=polit_1, y=ptg)) +
  geom_point()+
  geom_smooth(method="lm", level=0.89, formula=y~x)+
  theme(strip.text.x = element_text(color="black", size=20,face="bold" ))+ 
  ylab("Average Prestige Ratings")+
  xlab("Liberal Ideology")+
  theme (axis.title.y = element_text(color="black", size=20, face="bold"), axis.title.x = element_text(color="black", size=24, face="bold"))+theme_bw()+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_x_continuous(breaks = seq(1, 7, by = 1))+
  scale_y_continuous(breaks = seq(1, 7, by = 1))+
  ggtitle("Donald Trump")

d<-ggMarginal(Trump_ptg_polit, type = "histogram")

```

# CORRELATION LIBERAL IDEOLOGY- PERCEPTIONS OF HILLARY CLINTON AS DOMINANT

```{r}
cor(Hillary$dom, Hillary$polit_1)
```
```{r}
library(ggplot2)
library(ggExtra)

Hillary_dom_polit<-ggplot(Hillary, aes(x=polit_1, y=dom)) +
  geom_point()+
  geom_smooth(method="lm", level=0.89, formula=y~x)+
  theme(strip.text.x = element_text(color="black", size=20,face="bold" ))+ 
  ylab("Average Dominance Ratings")+
  xlab("Liberal Ideology")+
  theme (axis.title.y = element_text(color="black", size=20, face="bold"), axis.title.x = element_text(color="black", size=24, face="bold"))+theme_bw()+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_x_continuous(breaks = seq(1, 7, by = 1))+
  scale_y_continuous(breaks = seq(1, 7, by = 1))+
  ggtitle("Hillary Clinton")

e<-ggMarginal(Hillary_dom_polit, type = "histogram")

```

# CORRELATION LIBERAL IDEOLOGY- PERCEPTIONS OF DONALD TRUMP AS DOMINANT
```{r}
cor(Trump$dom, Trump$polit_1)
```
```{r}
library(ggplot2)
library(ggExtra)

Trump_dom_polit<-ggplot(Trump, aes(x=polit_1, y=dom)) +
  geom_point()+
  geom_smooth(method="lm", level=0.89, formula=y~x)+
  theme(strip.text.x = element_text(color="black", size=20,face="bold" ))+ 
  ylab("Average Dominance Ratings")+
  xlab("Liberal Ideology")+
  theme (axis.title.y = element_text(color="black", size=20, face="bold"), axis.title.x = element_text(color="black", size=24, face="bold"))+theme_bw()+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_x_continuous(breaks = seq(1, 7, by = 1))+
  scale_y_continuous(breaks = seq(1, 7, by = 1))+
  ggtitle("Donald Trump")

f<-ggMarginal(Trump_dom_polit, type = "histogram")

```

```{r}
library(gridExtra)
grid.arrange(c, d, e, f,  ncol=2) 
```