---
title: "Results_Elections"
author: "Angel V. Jimenez"
date: "25 July 2019"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

################################################################################################################
# ADDITIONAL STUDY: DID TRUMP WIN IN THE STATES WITH GREATER ECONOMIC UNCERTEINTY?
################################################################################################################

## ECONOMIC UNCERTAINTY = COMPOSITE MEASURE

Economic Uncerteinty = (HousingVacancy+AdultsnoWork+Poverty)/3

Data about economic uncerteinty downloaded from the 2016 Distress Comunities Index (http://eig.org/dci/interactive-maps/state-congressional-districts)

Data about election results downloaded from https://www.dailykos.com/stories/2016/11/25/1601042/-Nerd-Alert-This-spreadsheet-contains-every-presidential-election-by-state-from-1828-to-2016

Outcome: WinnerTrump=1, WinnerClinton=0
```{r}
elections<-read.csv("C://EcoUncer.csv")
str(elections)
head(elections)
```


```{r}
# Null model
model0<-glm(WinnerTrump~1,family=binomial(link='logit'),data=elections)
summary(model0)
```




```{r}
# Model 1: Predictor = Economic Uncerteinty = (HousingVacancy+AdultsnoWork+Poverty)/3
# Economic Uncertainty Model 
model1<-glm(WinnerTrump ~EcoUncer,family=binomial(link='logit'),data=elections)
summary(model1) # Economic Uncerteinty positively predicts the victory of Trump
#https://mgimond.github.io/Stats-in-R/Logistic.html
# pseudo.R2.model1
(pseudo.R2.model1 <- (model1$null.deviance - model1$deviance)/model1$null.deviance)
```

```{r}
# Political Ideology Model (% votes for Republicans in 2012)
model2<-glm(WinnerTrump ~Repshare2012,family=binomial(link='logit'),data=elections)
summary(model2)
#https://mgimond.github.io/Stats-in-R/Logistic.html
# pseudo.R2.model2
(pseudo.R2.model2 <- (model2$null.deviance - model2$deviance)/model2$null.deviance)
```

```{r}
#Full Model
model3<-glm(WinnerTrump ~EcoUncer + Repshare2012,family=binomial(link='logit'),data=elections)
summary(model3) 
#https://mgimond.github.io/Stats-in-R/Logistic.html
# pseudo.R2.model3
(pseudo.R2.model3 <- (model3$null.deviance - model3$deviance)/model3$null.deviance)
```



## ECONOMIC UNCERTAINTY = Poverty Rate, Housing Vacancy Rate, Unemployment Rate as separate predictors

```{r}
# Economic Uncertainty model with economic uncertainty variables introduced separately
model4<-glm(WinnerTrump ~ HousingVacancy+AdultsnoWrok+Poverty, family=binomial(link='logit'),data=elections)
summary(model4)
#https://mgimond.github.io/Stats-in-R/Logistic.html
# pseudo.R2.model4
(pseudo.R2.model4 <- (model4$null.deviance - model4$deviance)/model4$null.deviance)
```

```{r}
# Housing Vacancy
model5<-glm(WinnerTrump ~ HousingVacancy, family=binomial(link='logit'),data=elections)
summary(model5)
#https://mgimond.github.io/Stats-in-R/Logistic.html
# pseudo.R2.model5
(pseudo.R2.model5 <- (model5$null.deviance - model5$deviance)/model5$null.deviance)
```

```{r}
# Adults without work
model6<-glm(WinnerTrump ~ AdultsnoWrok, family=binomial(link='logit'),data=elections)
summary(model6)
#https://mgimond.github.io/Stats-in-R/Logistic.html
# pseudo.R2.model6
(pseudo.R2.model6 <- (model6$null.deviance - model6$deviance)/model6$null.deviance)
```

```{r}
# Poverty
model7<-glm(WinnerTrump ~ Poverty, family=binomial(link='logit'),data=elections)
summary(model7)
#https://mgimond.github.io/Stats-in-R/Logistic.html
# pseudo.R2.model7
(pseudo.R2.model7 <- (model7$null.deviance - model7$deviance)/model7$null.deviance)
```


```{r}
# Full model with economic uncertainty variables introduced separately
model8<-glm(WinnerTrump ~ Repshare2012 + HousingVacancy+AdultsnoWrok+Poverty, family=binomial(link='logit'),data=elections)
summary(model8)
#https://mgimond.github.io/Stats-in-R/Logistic.html
# pseudo.R2.model8
(pseudo.R2.model8 <- (model8$null.deviance - model8$deviance)/model8$null.deviance)
```

# Same models but with proportion of voting for trump as outcome variable (Binomial for proportional data)
## ECONOMIC UNCERTAINTY = COMPOSITE MEASURE
```{r}
elections$Trump_Proportion<-elections$Trump/100
```

```{r}
# Null model
model0<-glm(Trump_Proportion~1,family=binomial(link='logit'),data=elections)
summary(model0)
```


```{r}

# Economic Uncertainty Model 
model1<-glm(Trump_Proportion ~EcoUncer,family=binomial(link='logit'),data=elections)
summary(model1) # Economic Uncerteinty positively predicts the victory of Trump
#https://mgimond.github.io/Stats-in-R/Logistic.html
# pseudo.R2.model1
(pseudo.R2.model1 <- (model1$null.deviance - model1$deviance)/model1$null.deviance)

```

```{r}
# Political Ideology Model (% votes for Republicans in 2012)
model2<-glm(Trump_Proportion ~Repshare2012,family=binomial(link='logit'),data=elections)
summary(model2)
#https://mgimond.github.io/Stats-in-R/Logistic.html
# pseudo.R2.model2
(pseudo.R2.model2 <- (model2$null.deviance - model2$deviance)/model2$null.deviance)
```

```{r}
#Full Model
model3<-glm(Trump_Proportion ~EcoUncer + Repshare2012,family=binomial(link='logit'),data=elections)
summary(model3) 
#https://mgimond.github.io/Stats-in-R/Logistic.html
# pseudo.R2.model3
(pseudo.R2.model3 <- (model3$null.deviance - model3$deviance)/model3$null.deviance)
```

# Same models but with proportion of voting for trump as outcome variable (Binomial for proportional data)
## ECONOMIC UNCERTAINTY = Poverty Rate, Housing Vacancy Rate, Unemployment Rate as separate predictors

```{r}
# Economic Uncertainty model with economic uncertainty variables introduced separately
model4<-glm(Trump_Proportion ~ HousingVacancy+AdultsnoWrok+Poverty, family=binomial(link='logit'),data=elections)
summary(model4)
#https://mgimond.github.io/Stats-in-R/Logistic.html
# pseudo.R2.model4
(pseudo.R2.model4 <- (model4$null.deviance - model4$deviance)/model4$null.deviance)
```

```{r}
# Housing Vacancy
model5<-glm(Trump_Proportion ~ HousingVacancy, family=binomial(link='logit'),data=elections)
summary(model5)
#https://mgimond.github.io/Stats-in-R/Logistic.html
# pseudo.R2.model5
(pseudo.R2.model5 <- (model5$null.deviance - model5$deviance)/model5$null.deviance)
```

```{r}
# Adults without work
model6<-glm(Trump_Proportion ~ AdultsnoWrok, family=binomial(link='logit'),data=elections)
summary(model6)
#https://mgimond.github.io/Stats-in-R/Logistic.html
# pseudo.R2.model6
(pseudo.R2.model6 <- (model6$null.deviance - model6$deviance)/model6$null.deviance)
```

```{r}
# Poverty
model7<-glm(Trump_Proportion ~ Poverty, family=binomial(link='logit'),data=elections)
summary(model7)
#https://mgimond.github.io/Stats-in-R/Logistic.html
# pseudo.R2.model7
(pseudo.R2.model7 <- (model7$null.deviance - model7$deviance)/model7$null.deviance)
```


```{r}
# Full model with economic uncertainty variables introduced separately
model8<-glm(Trump_Proportion ~ Repshare2012 + HousingVacancy+AdultsnoWrok+Poverty, family=binomial(link='logit'),data=elections)
summary(model8)
#https://mgimond.github.io/Stats-in-R/Logistic.html
# pseudo.R2.model8
(pseudo.R2.model8 <- (model8$null.deviance - model8$deviance)/model8$null.deviance)
```



